\appendix{I}

\chapter{Experimental Proposals and Speculative Validation}

\section{EEG Phase Mapping and Temporal Collapse Density}

\begin{itemize}
  \item \textbf{Goal:} Map angular phase density $\tau(x,t)$ in real-time from cortical EEG.
  \item \textbf{Hypothesis:} Higher EEG coherence in alpha/gamma bands correlates with local temporal collapse acceleration.
  \item \textbf{Approach:} Measure changes in synchronization across scalp regions; treat coherence envelopes as $\rho_{\text{obs}}(x,t)$ analogues.
\end{itemize}

\section{Recursive Collapse Detection in Feedback Circuits}

\begin{itemize}
  \item \textbf{Goal:} Construct closed-loop neural networks or synthetic circuits that induce measurable collapse recursion.
  \item \textbf{Hypothesis:} Phase-locked feedback will produce quantized collapse harmonics.
  \item \textbf{Approach:} Use time-delayed input-output layers to mimic $\mathcal{R}[v_\theta]$ structure. Analyze loop susceptibility $\mathcal{L}(x,t)$ over iterations.
\end{itemize}

\section{Sensory Deprivation and Collapse Rate Flattening}

\begin{itemize}
  \item \textbf{Goal:} Track subjective and neural time dilation under minimal observational environments.
  \item \textbf{Hypothesis:} Decreased sensory input lowers $\rho_{\text{obs}}$, leading to $\frac{dT}{dt} \rightarrow 0$ in cortical zones.
  \item \textbf{Approach:} Use float tanks, dark rooms, or occlusion hoods. Capture EEG drift and subjective time assessments.
\end{itemize}

\section{Mirror Neurons and Observer Entrainment}

\begin{itemize}
  \item \textbf{Goal:} Identify whether mirror neuron systems contribute to collapse-phase synchronization across individuals.
  \item \textbf{Hypothesis:} Mirror system activation increases phase alignment, reducing $\Delta\theta(t)$ in observer dyads.
  \item \textbf{Approach:} Use fMRI + EEG hyperscanning on paired subjects performing imitation tasks. Analyze for $\frac{d}{dt} \Delta\theta \rightarrow 0$ convergence.
\end{itemize}

\section{Citation Candidates}

\begin{itemize}
  \item EEG phase-synchrony: Varela et al., 2001 (*The brainweb*)
  \item Neural entrainment: Thut et al., 2011 (*Entrainment of perceptually relevant brain oscillations*)
  \item Mirror neurons: Rizzolatti and Sinigaglia, 2016 (*The mirror mechanism*)
  \item Neural feedback loops: Friston, 2008 (*Hierarchical models in the brain*)
  \item Time perception neuroscience: Wittmann, 2009 (*The inner sense of time*)
\end{itemize}
